\begin{longtable}{llrr}
\caption{Model predictions for unseen labels\label{tab:unseen_labels}}\\
\toprule
Task & True Label (Unseen) & Predicted Label & Count \\
\midrule
\endfirsthead
\multicolumn{4}{c}{\textit{Table \thetable{} continued from previous page}} \\
\toprule
Task & True Label (Unseen) & Predicted Label & Count \\
\midrule
\endhead
\midrule
\multicolumn{4}{r}{\textit{Continued on next page}} \\
\endfoot
\bottomrule
\endlastfoot
\multicolumn{4}{l}{\textbf{Sample Host}} \\
\addlinespace[0.5em]
 & \textit{alouatta palliata} & \textit{Gorilla sp.} & 8 \\
 & \textit{gorilla beringei} & \textit{Gorilla sp.} & 4 \\
 & \textit{gorilla beringei beringei} & \textit{Gorilla sp.} & 16 \\
 & \textit{gorilla beringei graueri} & \textit{Gorilla sp.} & 8 \\
 & \textit{gorilla beringei graueri} & \textit{Homo sapiens neanderthalensis} & 4 \\
 & \textit{gorilla gorilla gorilla} & \textit{Gorilla sp.} & 5 \\
 & \textit{homo sapiens} & \textit{Homo sapiens} & 1 \\
 & \textit{lithobates pipiens} & \textit{Homo sapiens neanderthalensis} & 11 \\
 & \textit{pan troglodytes ellioti} & \textit{Pan troglodytes} & 4 \\
 & \textit{pan troglodytes schweinfurthii} & \textit{Pan troglodytes} & 7 \\
 & \textit{papio anubis} & \textit{Homo sapiens} & 3 \\
 & \textit{papio anubis} & \textit{Pan troglodytes} & 1 \\
 & \textit{papio hamadryas} & \textit{Homo sapiens} & 4 \\
 & \textit{papio hamadryas} & \textit{Gorilla sp.} & 1 \\
 & \textit{papio sp.} & \textit{Homo sapiens neanderthalensis} & 1 \\
 & \textit{unknown} & \textit{Homo sapiens neanderthalensis} & 1 \\
\addlinespace
\multicolumn{4}{l}{\textbf{Material}} \\
\addlinespace[0.5em]
 & Oral & tissue & 1 \\
 & Skin & skin & 18 \\
 & Skin & tooth & 2 \\
 & anterior nares & bone & 2 \\
 & birch pitch & sediment & 39 \\
 & birch pitch & skin & 30 \\
 & birch pitch & saliva & 7 \\
 & birch pitch & bone & 3 \\
 & brain & tissue & 1 \\
 & buccal mucosa & skin & 2 \\
 & dentine & bone & 1 \\
 & dentine & dental calculus & 1 \\
 & digestive\_contents & digestive tract contents & 1 \\
 & faeces & digestive tract contents & 16 \\
 & faeces & dental calculus & 1 \\
 & intestine & skin & 7 \\
 & intestine & bone & 3 \\
 & intestine & tooth & 1 \\
 & lake sediment & sediment & 81 \\
 & lake sediment & permafrost & 9 \\
 & lake sediment & tissue & 1 \\
 & marine sediment & sediment & 64 \\
 & marine sediment & shell & 2 \\
 & palaeofaeces & digestive tract contents & 3 \\
 & palaeofaeces & dental calculus & 1 \\
 & palaeofaeces & sediment & 1 \\
 & shallow marine sediment & sediment & 2 \\
 & shallow marine sediment & skin & 1 \\
 & tongue & skin & 2 \\
 & tongue & tissue & 2 \\
\addlinespace
\bottomrule
\end{longtable}
\addcontentsline{toc}{subsection}{Supplementary Table 2: Model predictions for unseen labels}
{\footnotesize Unseen labels are categories not present in the training set. Sample Host: Novel species/subspecies correctly mapped to genus/species-level training classes. Material: Novel material types mapped to semantically similar training classes. Sample Host: 79 unseen predictions. Material: 305 unseen predictions.}