\small
\begin{longtable}{@{}llrrll@{}}
\caption{BioProjects with the most high-confidence errors (confidence $\geq 0.9$, predicted $\neq$ true) in the full external validation set (987 runs), summed across all four classification tasks. This analysis diagnoses systematic, study-level sources of error.\label{tab:bioproject_offenders}}\\
\toprule
BioProject & Study & Val runs & Conf.\ errors & Main tasks$^{a}$ & Root cause \\
\midrule
\endfirsthead
\endhead
\bottomrule
\endlastfoot
\texttt{PRJNA994900} & Kirdok2024 & 70 & 141 & CT, Mat., SH & OOD material \\
\texttt{PRJEB34569} & FellowsYates2021 & 42 & 36 & SH & Taxonomic resolution \\
\texttt{PRJEB80877} & vonHippel2025 & 46 & 35 & Mat. & Label granularity \\
\texttt{PRJNA1211513} & Schreiber2025 & 48 & 34 & Mat. & Label granularity \\
\texttt{PRJEB49638} & Moraitou2022 & 20 & 24 & SH & Taxonomic resolution \\
\texttt{PRJEB74036} & Liu2024 & 21 & 17 & Mat. & Label granularity \\
\texttt{PRJEB33848} & Neukamm2020 & 24 & 16 & CT, Mat. & Label granularity \\
\texttt{PRJEB11419} & – & 10 & 15 & Mat., CT & OOD material \\
\texttt{PRJEB67998} & Bozzi2024 & 19 & 11 & Mat., CT & Label ambiguity \\
\texttt{PRJNA320875} & Graham2016 & 12 & 11 & Mat. & Label granularity \\
\end{longtable}
\addcontentsline{toc}{subsection}{Supplementary Table 9: BioProjects dominating high-confidence validation errors (full validation set)}
\\[2mm]
{\footnotesize Counts use the full validation set (987 runs), including runs whose true labels are outside DIANA's label set; see Table~\ref{tab:performance} for seen-label-only metrics. $^{a}$~Task abbreviations: ST\,=\,Sample Type, CT\,=\,Community Type, SH\,=\,Sample Host, Mat.\,=\,Material. Root-cause categories --- \textit{OOD material}: material class absent from DIANA training classes; \textit{Label granularity}: external label is a subtype of a DIANA class (e.g.\ lake/marine sediment vs.\ sediment); \textit{Taxonomic resolution}: subspecies-level true label vs.\ genus/species-level DIANA outputs (e.g.\ \textit{gorilla beringei beringei} vs.\ \textit{Gorilla sp.}); \textit{Label ambiguity}: confusion among similar classes all present in training (e.g.\ tooth vs.\ bone); \textit{Genuine confusion}: label is in DIANA's label set but the model still predicts confidently incorrectly.}